### 2016-04-02 doc/publications/plos16/plos16.tex
Just updated
added PLOS-submission.pdf as it was not being created automatically for me
added section on variable selection, figures, bibliography

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

We therefore we developed CursedForest a Spark-based random forest algorithm able to process big and `wide' data. Unlike the standard Apache implementation, CursedForest is able to easily process data with millions of dimensions without excessive resource requirements on the driver or worker nodes.
%Also, due to more efficient handling of high-dimensional data, equivalent jobs are likely to finish faster on wideML than Spark ML.
In the fist section we

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Methods}
\subsection*{VariantSpark.}

@@

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\begin{thebibliography}{10}
\bibitem{bib1}
Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi: 10.1016/j.molimm.2014.11.005

\bibitem{bib2}
Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.

\end{thebibliography}

>>>>

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

We therefore we developed CursedForest a Spark-based random forest algorithm able to process big and `wide' data. Unlike the standard Apache implementation, CursedForest is able to easily process data with millions of dimensions without excessive resource requirements on the driver or worker nodes.
%Also, due to more efficient handling of high-dimensional data, equivalent jobs are likely to finish faster on wideML than Spark ML.
In the first section we

\section*{Variable Selection Using Random Forests}

\cite{Biau.2012} provide a proof that a random forest model will converge at a rate that depends on the cardinality of
the set $S$ of  ``strong predictors'' rather than on the number of variables $p$. That is, given a function $y=f(S)$
depending on a set of variables $S$, a random forest will converge to the true function $y$ with a rate that depends on
the size of $S$ and not the number of noise variables in the data set. If the size of $S$ is small compared to the total
number of variables, then the rate of convergence will be quicker.

In a number of simulations (reproduced from \cite{Genuer.et.al.2010}) we see evidence that random forests can recover
the variables defining a functional relationship in the presence of a substantial number of noise variables. See the
supplementary information for full details. It is apparently that some of the model parameters, such
as \texttt{mtry} -- the number of randomly selected variables considered as potential splits at each node, have to be altered
from their default value when there are a large number of predictors.

It is likely that in the genomic setting, variables will have a monotonic influence on the outcome. 
We have taken \cite{Genuer.et.al.2010}'s tree function example and extended it to a much larger number of noise variables.
The function, shown in figure  \ref{figure:tree_function.png}, is 
defined on the first 5 predictor variables. We have added Gaussian noise to the function (figure \ref{figure:noisy_tree_function.png})
and extended the size of the training data set from $n=100 \times p=1000$ to $n=100 \times  p=1000000$.
The random forest model recovers variables 1 and 4 as the two
most important variables (out of 1000000). It fails to uncover the other 3 variables, $\{2,3,5\}$.

It would appear that even in setting with an extremely large number of noise variables, it may be possible to recover
the significant varaiables if the functional relationship is simple.

\begin{figure}[tbhp]
 \includegraphics[totalheight=9cm]{./figs/tree_function.png}
 \captionof{figure}{The tree function.}
  \label{figure:tree_function.png}
\end{figure}

\begin{figure}[tbhp]
 \includegraphics[totalheight=8cm]{./figs/noisy_tree_function.png}
 \captionof{figure}{A plot of the ordered $y$ variable for the tree example, and the $y$ variable with added Gaussian
   noise (in red).}
  \label{figure:noisy_tree_function.png}
\end{figure}

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Methods}

\subsection*{VariantSpark.}

@@

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%

\bibliography{./CursedForest.bib}
